Simulation Study of Angular Resolution of a New Electromagnetic Sampling Calorimeter

### 2022-02-07 paper.tex
updates

The sampling fluctuation can be improved by optimizing the thickness ratio of the absorber to the active medium. A 5-m-long cylindrical calorimeter made of alternating layers of Pb and plastic scintillating plates is an example of the sampling calorimeter~\cite{E391a_barrel}.

The segmented structure of the active medium facilitates the measurement of lateral distributions of the EM shower along the incident photon direction. The photon direction can also be deduced from the information on the EM shower shape. The measurement of photon directions can help predict photon production vertices, which is crucial for the background suppression in KOTO experiment~\cite{KOTOproposal}.

>>>>

The sampling fluctuation can be improved by optimizing the thickness ratio of the absorber to the active medium. A 3-m-long cylindrical calorimeter made of alternating layers of Pb and plastic scintillating plates is an example of the sampling calorimeter~\cite{Murayama:2020mcp}.

The segmented structure of the active medium facilitates the measurement of lateral distributions of the EM shower along the incident photon direction. The photon direction can also be deduced from the information on the EM shower shape. The measurement of photon directions can help predict photon production vertices, which is crucial for the background suppression in KOTO experiment~\cite{KOTO:2012}.
